Supermassive black holes and their host spheroids \\ III. The $M_{\rm BH} - \lowercase{n_{\rm sph}}$ correlation

### 2016-02-24 papers/mbhn/replytoreferee.txt

I thank the referee for a prompt and insightful review that helped improve the quality of the manuscript. 
I have modified the manuscript as suggested by the referee, and highlighted the changes in boldface. 
Below is my response to the referee report.

Figures 1 and 2 have been modified to show the insets with error bars on the same scale as the main plots. 
I wish to maintain the fancy symbols for continuity with Paper II and because they allow to identify 
the two lenticular galaxies excluded from the linear regression analysis (orange crosses) and
the four galaxies classified as E/S0 or S0/Sp. 
If I was to show only the four-colour error bars, these six data points could not be easily located. 
I tried to combine fancy symbols and error bars in a single panel, but the result was a messy and 
too "crowded" plot. 
Hopefully a two-panel figure - with separate symbols and error bars - is a good compromise.

The linear regression for the "all" sample is now shown with a black dotted line in both Figures 1 and 2. 
Indeed, the Figures are now more informative. 
Looking at the bottom panel of Figure 1, one can notice that the blue and orange error bars 
span basically the same range in spheroid magnitude and Sérsic index, but they are offset from each other. 
In effect, the L-n linear regression for all galaxies seems to almost exactly define a separation line 
in between lenticular and spiral galaxies. 
Going beyond a "by eye" assessment, the linear regression analysis, which takes into account the error bars, 
confirms that the slopes of the correlations for early- and late-type galaxies are not consistent with each other
within their 1 sigma uncertainties. 
This is already a quantitative indication that early- and late-type galaxies define two separate L-n sequences, 
which justifies the use of a 4-parameter model, rather than a 2-parameter one, to describe the L-n diagram. 
I've also explored an independent method, drawn from Information Theory, to measure the relative quality of 
a 2-parameter and a 4-parameter model for the given L-n dataset. 
The Akaike Information Criterion rewards the goodness of a fit and penalises the number of parameter used 
in the model, therefore it provides a means for model selection. 
The Akaike Information Criterion test confirms that a 4-parameter model is preferred over a 2-parameter model 
to describe the L-n diagram, whereas a 2-parameter model is preferred over a 4-parameter model to describe 
the Mbh-n dataset. 
Details about the Akaike Information Criterion are given in the manuscript (Section 3.1).

Indeed, I agree with the referee's concern about the uncertain and sometimes misleading definition of "bulge" 
adopted in the literature, which led us to prefer the use of a more general term such as "spheroid" as opposed 
to disk, although we recognise that "spheroid" might not be fully appropriate to describe disk-like pseudobulges. 
In Papers I, II and III, as long as in Savorgnan & Graham (2016, MNRAS, 457, 320), we adopted and tried to be 
consistent with a point of view similar to that of the ATLAS3D team: local galaxies display a continuous distribution 
of spheroid-to-total flux ratios (e.g. Figure 2 of Cappellari et al. 2011), going from disc-less, "pure" 
elliptical galaxies (slow rotators) to disc-dominated lenticular and spiral galaxies (fast rotators). 
In Paper I, we consistently modelled each galaxy's spheroid with a Sérsic profile. Our identification of the spheroidal 
component can be classified as a "photometric" identification: we associated the spheroidal component with the central 
excess of light after the subtraction of discs, bars, nuclei, rings and disc-like components.

Since it was first presented in 2007 by Graham & Driver, the Mbh-n correlation did not receive enough attention 
over the following years. Vika et al. and Beifiori et al. failed to recover the correlation, whereas Sani et al. 
and Lasker et al. didn't even explore the Mbh-n diagram (and we checked that no strong Mbh-n correlation 
could be obtained using their datasets). 
In addition, none of these works explored the L-n diagram, whose more recent analysis was done by us (to our best knowledge) 
in Savorgnan et al. (2013) using the Graham & Guzman (2003) and Graham & Worley (2008) (outdated) datasets. 
For this reason, we felt that joining the analysis of the Mbh-n correlation with that of the more popular Mbh-L 
correlation would not have given enough credit to the former. 
At present, no simulations of black hole-galaxy coevolution take into account the observed Mbh-n correlation. 
A separate analysis and a dedicated manuscript would therefore give more visibility to this relation.
A separate analysis is also motivated by the following fact. The three linear regression routines 
(BCES, mFITEXY and linmix_err) all gave consistent results for the Mbh-L correlation. 
However, as explained in Section 3 of the manuscript, the modified FITEXY routine performs better than the BCES and 
linmix_err codes when it comes to the analysis of our L-n and Mbh-n datasets. 
To avoid confusion, we preferred to keep the analyses of the Mbh-L and Mbh-n relations separate.

### 2016-02-24 papers/mbhn/mbhn.tex
referee report mbhn

\begin{abstract}
The S\'ersic $R^{1/n}$ model is the best approximation known to date for describing the light distribution of stellar spheroidal and disk components, 
with the S\'ersic index $n$ providing a direct measure of the central radial concentration of stars. 
The S\'ersic index of a galaxy's spheroidal component, $n_{\rm sph}$, has been shown to tightly correlate 
with the mass of the central supermassive black hole, $M_{\rm BH}$. 
The $M_{\rm BH} - n_{\rm sph}$ correlation is also expected from other two well known scaling relations 
involving the spheroid luminosity, $L_{\rm sph}$: 
the $L_{\rm sph} - n_{\rm sph}$ and the $M_{\rm BH} - L_{\rm sph}$. 
Obtaining an accurate estimate of the spheroid S\'ersic index requires a careful modelling of a galaxy's light distribution 
and some studies have failed to recover a statistically significant $M_{\rm BH} - n_{\rm sph}$ correlation. 
With the aim of re-investigating the $M_{\rm BH} - n_{\rm sph}$ 
and other black hole mass scaling relations, 
we performed a detailed (i.e.~bulge, disks, bars, spiral arms, rings, halo, nucleus, etc.) 
decomposition of 66 galaxies, with directly measured black hole masses, 
that had been imaged at $3.6\rm~\mu m$ with \emph{Spitzer}. 
In this paper, the third of this series, we present an analysis of the $L_{\rm sph} - n_{\rm sph}$ and $M_{\rm BH} - n_{\rm sph}$ diagrams. 
While early-type (elliptical+lenticular) and late-type (spiral) galaxies split into two separate relations 
in the $L_{\rm sph} - n_{\rm sph}$ and $M_{\rm BH} - L_{\rm sph}$ diagrams, 
they reunite into a single $M_{\rm BH} \propto n_{\rm sph}^{3.39 \pm 0.15}$ sequence
with relatively small intrinsic scatter ($\epsilon_{(M_{\rm BH} | n_{\rm sph})} \simeq 0.25 \rm~dex$). 
The black hole mass appears to be closely related to the spheroid central concentration of stars, 
which mirrors the inner gradient of the spheroid gravitational potential. 
\end{abstract}

@@

\subsection{$L_{\rm sph} - n_{\rm sph}$}
Following \cite{graham2001bulges}, 
who showed that the $L_{\rm sph} - n_{\rm sph}$ relation is different for elliptical galaxies and the bulges of disk galaxies (S0+Sp), 
\cite{savorgnan2013} re-analyzed the data from \cite{grahamguzman2003} and \cite{grahamworley2008} 
and obtained two separate $L_{\rm sph} - n_{\rm sph}$ linear regressions for elliptical galaxies and the bulges of disk galaxies 
(in the B- and K-band, respectively). 
At the time, the $L_{\rm sph} - n_{\rm sph}$ datasets from \cite{grahamguzman2003} and \cite{grahamworley2008} were of the best quality available 
to investigate the $L_{\rm sph} - n_{\rm sph}$ relation for different galaxy morphological types. 
However, these datasets were not obtained from a homogeneous analysis, 
but they were a collection of results taken from various past bulge/disk decomposition studies. 
%It is also worth mentioning that, 
%although the K-band luminosities of the bulges of disk galaxies had been corrected for internal dust absorption, 
%{\bf such corrections are still not very accurate today?!? Driver et al. xxxx??? }  
Here we re-investigate the $L_{\rm sph} - n_{\rm sph}$ diagram using only our high-quality dataset. 
Our spheroid luminosities and S\'ersic indices were obtained from accurate multicomponent decompositions,  
performed in a consistent manner using the $3.6\rm~\mu m$ band, which is less affected by dust extinction than the K-band. \\
\cite{grahamworley2008} presented a single $L_{\rm sph} - n_{\rm sph}$ correlation for the bulges of disk galaxies (S0+Sp).
However, using our dataset, 
we fit the $L_{\rm sph} - n_{\rm sph}$ relation for elliptical, lenticular and spiral galaxies separately, 
and found that the values of the slope and intercept for the lenticular galaxies 
are not consistent within the errors with those for the spiral galaxies, 
but are consistent within the errors with those for the elliptical galaxies.  
Given this, we conclude that in the $L_{\rm sph} - n_{\rm sph}$ diagram 
elliptical and lenticular galaxies form together a single (\emph{early-type}) sequence, 
whereas the combination of lenticular and spiral galaxies do not. 
According to the modified FITEXY routine, 
early-type galaxies\footnote{Using the BCES estimator, 
\cite{savorgnan2013} re-analyzed the dataset from \cite{grahamguzman2003} 
and obtained $L_{\rm sph} \propto n_{\rm sph}^{3.60 \pm 0.19}$ for the elliptical galaxies only. 
This result is in excellent agreement with the BCES linear regression obtained here for the early-type galaxies 
($L_{\rm sph} \propto n_{\rm sph}^{3.89 \pm 0.42}$) 
and, remarkably, it is exactly the same proportionality obtained here for the early-type galaxies with the modified FITEXY routine. } 
follow $L_{\rm sph} \propto n_{\rm sph}^{3.60 \pm 0.19}$, 
whereas late-type galaxies follow a shallower $L_{\rm sph} \propto n_{\rm sph}^{1.44 \pm 0.52}$ sequence.

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/mag_vs_n_maj.pdf}
\caption{Spheroid absolute magnitude (at $3.6\rm~\mu m$) plotted against spheroid S\'ersic index 
measured along the galaxy major-axis. 
Symbols are coded according to the galaxy morphological type (see legend).
The orange crosses denote two lenticular galaxies (NGC 0524 and NGC 3998) which were excluded from the linear regression analysis 
(see Section \ref{sec:anal}). 
The red dashed line indicates the FITEXY bisector linear regression for the $45-2=43$  early-type galaxies (E+S0), 
with the red shaded area denoting its $1\sigma$ uncertainty. 
The shallower blue solid line shows the FITEXY bisector linear regression for the bulges of the 17 late-type (Sp) galaxies, 
with the blue shaded area denoting its $1\sigma$ uncertainty. 
The inset panel shows the error bars associated to each data point,  
where the error bars have the same color coding as the symbols in the main figure. 
}
\label{fig:magn}
\end{center}
\end{figure}

\subsection{$M_{\rm BH} - n_{\rm sph}$}
\cite{grahamscott2013} presented two different $M_{\rm BH} - L_{\rm sph}$ relations for S\'ersic and core-S\'ersic 
spheroids\footnote{Core-S\'ersic spheroids have partially depleted cores relative to their outer S\'ersic light profile, 
whereas S\'ersic spheroids have no central deficit of stars. } \citep{graham2003coresersicmodel,trujillo2004coresersicmodel}.
However, in \emph{Paper II} we found that the slopes of the $M_{\rm BH} - L_{\rm sph}$ correlations for S\'ersic and core-S\'ersic spheroids 
are consistent with each other within their $1\sigma$ uncertainties, 
which prevented us from considering them as two separate sequences. 
On the other hand, our analysis showed that early- and late-type galaxies follow two different $M_{\rm BH} - L_{\rm sph}$ relations. 
%($M_{\rm BH} \propto L_{\rm sph}^{1.00 \pm 0.10}$ 
%and $M_{\rm BH} \propto L_{\rm sph}^{2.88 \pm 0.68}$, respectively). \\
Given that early- and late-type galaxies define two separate sequences in both the $L_{\rm sph} - n_{\rm sph}$ 
and $M_{\rm BH} - L_{\rm sph}$ diagrams, 
we investigate substructure in the $M_{\rm BH} - n_{\rm sph}$ diagram. 
Using the results from the modified FITEXY routine, 
we know that the early-type galaxies follow $M_{\rm BH} \propto L_{\rm sph}^{1.03 \pm 0.11}$ 
and $L_{\rm sph} \propto n_{\rm sph}^{3.60 \pm 0.19}$, 
therefore we expect to find $M_{\rm BH} \propto n_{\rm sph}^{3.69 \pm 0.44}$; 
this prediction is in excellent agreement with the observed log-slope of $3.58 \pm 0.27$ obtained here. 
On the other hand, late-type galaxies follow $M_{\rm BH} \propto L_{\rm sph}^{2.58 \pm 1.06}$ 
and $L_{\rm sph} \propto n_{\rm sph}^{1.44 \pm 0.52}$, 
from which one can predict $M_{\rm BH} \propto n_{\rm sph}^{3.72 \pm 2.03}$; 
this is consistent with the observed log-slope of $4.55 \pm 0.66$. 
The Bayesian estimator {\tt linmix\_err} returns consistent results: 
a log-slope of $3.44 \pm 0.33$ for the early-type galaxies 
and a log-slope of $4.12 \pm 1.07$ for the late-type galaxies. 
Regardless of the linear regression routine used, 
the values of the slope and intercept for the early- and late-type galaxies 
are consistent with each other within their $1\sigma$ uncertainties\footnote{In effect, 
considering the results of the modified FITEXY routine, 
the slopes of the relations for early- and late-type galaxies 
are only marginally consistent with each other within their $1\sigma$ uncertainties. 
However, the same slopes obtained with Bayesian estimator {\tt linmix\_err} 
are fully consistent with each other within their $1\sigma$ uncertainties. }.
Our analysis shows that the early- and late-type galaxies do not follow two separate trends in the $M_{\rm BH} - n_{\rm sph}$ diagram, 
i.e.~we do not identify any significant substructure based on the galaxy morphological type. \\
The symmetrical linear regression for all galaxies obtained with the modified FITEXY routine is: 
\begin{equation*}
\log \biggl( \frac{M_{\rm BH}}{\rm M_\odot} \biggr) = (8.15 \pm 0.06) + (3.37 \pm 0.15) \bigl(\log n_{\rm sph} - 0.50 \bigr) . 
\end{equation*}
\\

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/mbh_vs_n_maj.pdf}
\caption{Black hole mass plotted against spheroid S\'ersic index measured along the galaxy major-axis. 
Symbols are coded according to the galaxy morphological type (see legend). 
The orange crosses denote two lenticular galaxies (NGC 0524 and NGC 3998) which were excluded from the linear regression analysis 
(see Section \ref{sec:anal}). 
The red dashed line indicates the FITEXY bisector linear regression for the $45-2=43$  early-type galaxies (E+S0), 
with the red shaded area denoting its $1\sigma$ uncertainty. 
The shallower blue solid line shows the FITEXY bisector linear regression for the bulges of the 17 late-type (Sp) galaxies, 
with the blue shaded area denoting its $1\sigma$ uncertainty. 
The linear regressions for early- and late-type galaxies are consistent with each other within their $1\sigma$ uncertainties.  
The inset panel shows the error bars associated to each data point,  
where the error bars have the same color coding as the symbols in the main figure. 
}
\label{fig:mbhn}
\end{center}
\end{figure}

@@

%%
\acknowledgments
GS warmly thanks Alister Graham and Carlo Nipoti for useful discussion. 
%We also thank the anonymous referee for useful comments and suggestions. 
This research was supported by Australian Research Council funding through grants
DP110103509 and FT110100263.
This work is based on observations made with the IRAC instrument \citep{fazio2004IRAC} 
on-board the Spitzer Space Telescope, 
which is operated by the Jet Propulsion Laboratory, 
California Institute of Technology under a contract with NASA.
This research has made use of the GOLDMine database \citep{goldmine} and the NASA/IPAC Extragalactic Database (NED) 
which is operated by the Jet Propulsion Laboratory, California Institute of Technology, 
under contract with the National Aeronautics and Space Administration. 
We acknowledge the usage of the HyperLeda database (\url{http://leda.univ-lyon1.fr}).
The BCES routine \citep{akritasbershady1996} was run via the python module 
written by Rodrigo Nemmen \citep{nemmen2012}, which is available at \url{https://github.com/rsnemmen/BCES}.
The modified FITEXY linear regressions were performed using the IDL routine MPFITEXY \citep{williams2010}, 
which is available at \url{http://purl.org/mike/mpfitexy}. 
The MPFITEXY routine depends on the MPFIT package \citep{markwardt2009}.

>>>>

\begin{abstract}
The S\'ersic $R^{1/n}$ model is the best approximation known to date for describing the light distribution 
of stellar spheroidal and disk components, 
with the S\'ersic index $n$ providing a direct measure of the central radial concentration of stars. 
The S\'ersic index of a galaxy's spheroidal component, $n_{sph}$, has been shown to tightly correlate 
with the mass of the central supermassive black hole, $M_{BH}$. 
The $M_{BH}-n_{sph}$ correlation is also expected from other two well known scaling relations 
involving the spheroid luminosity, $L_{sph}$: 
the $L_{sph}-n_{sph}$ and the $M_{BH}-L_{sph}$. 
Obtaining an accurate estimate of the spheroid S\'ersic index requires a careful modelling of a galaxy's light distribution 
and some studies have failed to recover a statistically significant $M_{BH}-n_{sph}$ correlation. 
With the aim of re-investigating the $M_{BH}-n_{sph}$ 
and other black hole mass scaling relations, 
we performed a detailed (i.e.~bulge, disks, bars, spiral arms, rings, halo, nucleus, etc.) 
decomposition of 66 galaxies, with directly measured black hole masses, 
that had been imaged at $3.6\rm~\mu m$ with \emph{Spitzer}. 
In this paper, the third of this series, we present an analysis of the $L_{sph}-n_{sph}$ 
and $M_{BH}-n_{sph}$ diagrams. 
While early-type (elliptical+lenticular) and late-type (spiral) galaxies split into two separate relations 
in the $L_{sph}-n_{sph}$ and $M_{BH}-L_{sph}$ diagrams, 
they reunite into a single $M_{BH} \propto n_{sph}^{3.39 \pm 0.15}$ sequence
with relatively small intrinsic scatter ($\epsilon \simeq 0.25 \rm~dex$). 
The black hole mass appears to be closely related to the spheroid central concentration of stars, 
which mirrors the inner gradient of the spheroid gravitational potential. 
\end{abstract}

@@

\subsection{$L_{\rm sph} - n_{\rm sph}$}
Following \cite{graham2001bulges}, 
who showed that the $L_{\rm sph} - n_{\rm sph}$ relation is different for elliptical galaxies and the bulges of disk galaxies (S0+Sp), 
\cite{savorgnan2013} re-analyzed the data from \cite{grahamguzman2003} and \cite{grahamworley2008} 
and obtained two separate $L_{\rm sph} - n_{\rm sph}$ linear regressions for elliptical galaxies and the bulges of disk galaxies 
(in the B- and K-band, respectively). 
At the time, the $L_{\rm sph} - n_{\rm sph}$ datasets from \cite{grahamguzman2003} and \cite{grahamworley2008} were of the best quality available 
to investigate the $L_{\rm sph} - n_{\rm sph}$ relation for different galaxy morphological types. 
However, these datasets were not obtained from a homogeneous analysis, 
but they were a collection of results taken from various past bulge/disk decomposition studies. 
%It is also worth mentioning that, 
%although the K-band luminosities of the bulges of disk galaxies had been corrected for internal dust absorption, 
%{\bf such corrections are still not very accurate today?!? Driver et al. xxxx??? }  
Here we re-investigate the $L_{\rm sph} - n_{\rm sph}$ diagram (Figure \ref{fig:magn}) using only our high-quality dataset. 
Our spheroid luminosities and S\'ersic indices were obtained from accurate multicomponent decompositions,  
performed in a consistent manner using the $3.6\rm~\mu m$ band, which is less affected by dust extinction than the K-band. \\
\cite{grahamworley2008} presented a single $L_{\rm sph} - n_{\rm sph}$ correlation for the bulges of disk galaxies (S0+Sp).
However, using our dataset, 
we fit the $L_{\rm sph} - n_{\rm sph}$ relation for elliptical, lenticular and spiral galaxies separately, 
and found that the values of the slope and intercept for the lenticular galaxies 
are not consistent within the errors with those for the spiral galaxies, 
but are consistent within the errors with those for the elliptical galaxies.  
Given this, we conclude that in the $L_{\rm sph} - n_{\rm sph}$ diagram 
elliptical and lenticular galaxies form together a single (\emph{early-type}) sequence, 
whereas the combination of lenticular and spiral galaxies do not. 
According to the modified FITEXY routine, 
early-type galaxies\footnote{Using the BCES estimator, 
\cite{savorgnan2013} re-analyzed the dataset from \cite{grahamguzman2003} 
and obtained $L_{\rm sph} \propto n_{\rm sph}^{3.60 \pm 0.19}$ for the elliptical galaxies only. 
This result is in excellent agreement with the BCES linear regression obtained here for the early-type galaxies 
($L_{\rm sph} \propto n_{\rm sph}^{3.89 \pm 0.42}$) 
and, remarkably, it is exactly the same proportionality obtained here for the early-type galaxies with the modified FITEXY routine. } 
follow $L_{\rm sph} \propto n_{\rm sph}^{3.60 \pm 0.19}$, 
whereas late-type galaxies follow a shallower $L_{\rm sph} \propto n_{\rm sph}^{1.44 \pm 0.52}$ sequence. \\
{\bf Because the log-slopes of the correlations for early- and late-type galaxies are not consistent with each other 
within their $1\sigma$ uncertainties, 
our quantitative linear regression analysis suggests that 
the $L_{\rm sph} - n_{\rm sph}$ diagram is better described with a four-parameter model 
(two separate power-laws) 
rather than with a two-parameter model (single power-law). 
In addition, the relative quality of these two statistical models can be independently assessed 
using the Akaike Information Criterion ($AIC$, \citealt{akaike1974}). 
$AIC$ is a trade-off between the statistical significance of a fit and the complexity of the model used. 
It benefits from the goodness of a fit, 
but at the same time is also penalized by the number of parameters of the model, 
hence it discourages overfitting. 
The $AICc$ is a variation of the $AIC$ that takes into account a correction for finite sample sizes: 
\begin{equation}
AICc = 2k - 2 \ln(\mathcal{L}) + \frac{2k (k+1)}{n-k-1} ,
\end{equation}
where $k$ is the number of parameter of the model, 
$n$ is the sample size, 
and $\mathcal{L}$ is the maximum value of the likelihood function for the model. 
Within a set of candidate models for a given dataset, 
the best model has the smallest $AICc$ value. 
Using our $L_{\rm sph} - n_{\rm sph}$ dataset, 
the $AICc$ value for a double power-law model is a factor of $3/4$ smaller 
than the $AICc$ value for a single power-law model. }

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth, trim = 20 0 220 0]{images/mag_vs_n_maj.pdf}
\caption{\bf Spheroid absolute magnitude (at $3.6\rm~\mu m$) plotted against spheroid S\'ersic index 
measured along the galaxy major-axis. 
The top and bottom panels show the data points and their error bars, respectively.  
Symbols are coded according to the galaxy morphological type (see legend in the top panel).
The orange crosses denote two lenticular galaxies (NGC 0524 and NGC 3998) which were excluded from the linear regression analysis 
(see Section \ref{sec:anal}). 
The black dotted line is the FITEXY bisector linear regression for all ($64$) galaxies, 
with the gray shaded area denoting its $1\sigma$ uncertainty. 
The red dashed line is the FITEXY bisector linear regression for the $45-2=43$  early-type galaxies (E+S0), 
with the red shaded area denoting its $1\sigma$ uncertainty. 
The shallower blue solid line is the FITEXY bisector linear regression for the bulges of the 17 late-type (Sp) galaxies, 
with the blue shaded area denoting its $1\sigma$ uncertainty. 
The error bars in the bottom panel have the same color coding as the symbols in the top panel. 
}
\label{fig:magn}
\end{center}
\end{figure}

\subsection{$M_{\rm BH} - n_{\rm sph}$}
\cite{grahamscott2013} presented two different $M_{\rm BH} - L_{\rm sph}$ relations for S\'ersic and core-S\'ersic 
spheroids\footnote{Core-S\'ersic spheroids have partially depleted cores relative to their outer S\'ersic light profile, 
whereas S\'ersic spheroids have no central deficit of stars. } \citep{graham2003coresersicmodel,trujillo2004coresersicmodel}.
However, in \emph{Paper II} we found that the slopes of the $M_{\rm BH} - L_{\rm sph}$ correlations for S\'ersic and core-S\'ersic spheroids 
are consistent with each other within their $1\sigma$ uncertainties, 
which prevented us from considering them as two separate sequences. 
On the other hand, our analysis showed that early- and late-type galaxies follow two different $M_{\rm BH} - L_{\rm sph}$ relations. 
%($M_{\rm BH} \propto L_{\rm sph}^{1.00 \pm 0.10}$ 
%and $M_{\rm BH} \propto L_{\rm sph}^{2.88 \pm 0.68}$, respectively). \\
Given that early- and late-type galaxies define two separate sequences in both the $L_{\rm sph} - n_{\rm sph}$ 
and $M_{\rm BH} - L_{\rm sph}$ diagrams, 
we investigate substructure in the $M_{\rm BH} - n_{\rm sph}$ diagram. 
Using the results from the modified FITEXY routine, 
we know that the early-type galaxies follow $M_{\rm BH} \propto L_{\rm sph}^{1.03 \pm 0.11}$ 
and $L_{\rm sph} \propto n_{\rm sph}^{3.60 \pm 0.19}$, 
therefore we expect to find $M_{\rm BH} \propto n_{\rm sph}^{3.69 \pm 0.44}$; 
this prediction is in excellent agreement with the observed log-slope of $3.58 \pm 0.27$ obtained here. 
On the other hand, late-type galaxies follow $M_{\rm BH} \propto L_{\rm sph}^{2.58 \pm 1.06}$ 
and $L_{\rm sph} \propto n_{\rm sph}^{1.44 \pm 0.52}$, 
from which one can predict $M_{\rm BH} \propto n_{\rm sph}^{3.72 \pm 2.03}$; 
this is consistent with the observed log-slope of $4.55 \pm 0.66$. 
The Bayesian estimator {\tt linmix\_err} returns consistent results: 
a log-slope of $3.44 \pm 0.33$ for the early-type galaxies 
and a log-slope of $4.12 \pm 1.07$ for the late-type galaxies. 
Regardless of the linear regression routine used, 
the values of the slope and intercept for the early- and late-type galaxies 
are consistent with each other within their $1\sigma$ uncertainties\footnote{In effect, 
considering the results of the modified FITEXY routine, 
the slopes of the relations for early- and late-type galaxies 
are only marginally consistent with each other within their $1\sigma$ uncertainties. 
However, the same slopes obtained with Bayesian estimator {\tt linmix\_err} 
are fully consistent with each other within their $1\sigma$ uncertainties. }.
Our analysis shows that the early- and late-type galaxies do not follow two separate trends 
in the $M_{\rm BH} - n_{\rm sph}$ diagram, 
i.e.~we do not identify any significant substructure based on the galaxy morphological type. 
{\bf The $AICc$ value for a single power-law model is a factor of $2/3$ smaller 
than the $AICc$ value for a double power-law model. } \\
The symmetrical linear regression for all galaxies obtained with the modified FITEXY routine is: 
\begin{equation*}
\log \biggl( \frac{M_{\rm BH}}{\rm M_\odot} \biggr) = (8.15 \pm 0.06) + (3.37 \pm 0.15) \bigl(\log n_{\rm sph} - 0.50 \bigr) . 
\end{equation*}
\\

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth, trim = 20 0 220 0]{images/mbh_vs_n_maj.pdf}
\caption{\bf Black hole mass plotted against spheroid S\'ersic index measured along the galaxy major-axis. 
The top and bottom panels show the data points and their error bars, respectively.  
Symbols are coded according to the galaxy morphological type (see legend). 
The orange crosses denote two lenticular galaxies (NGC 0524 and NGC 3998) which were excluded from the linear regression analysis 
(see Section \ref{sec:anal}). 
The black dotted line is the FITEXY bisector linear regression for all ($64$) galaxies, 
with the gray shaded area denoting its $1\sigma$ uncertainty. 
The red dashed line is the FITEXY bisector linear regression for the $45-2=43$  early-type galaxies (E+S0), 
with the red shaded area denoting its $1\sigma$ uncertainty. 
The blue solid line is the FITEXY bisector linear regression for the bulges of the 17 late-type (Sp) galaxies, 
with the blue shaded area denoting its $1\sigma$ uncertainty. 
The linear regressions for early- and late-type galaxies are consistent with each other within their $1\sigma$ uncertainties.  
The error bars in the bottom panel have the same color coding as the symbols in the top panel. 
}
\label{fig:mbhn}
\end{center}
\end{figure}

@@

%%
\acknowledgments
GS warmly thanks Chris Blake, Alister Graham and Carlo Nipoti for useful discussion. 
We also thank the anonymous referee for useful comments and suggestions. 
This research was supported by Australian Research Council funding through grants
DP110103509 and FT110100263.
This work is based on observations made with the IRAC instrument \citep{fazio2004IRAC} 
on-board the Spitzer Space Telescope, 
which is operated by the Jet Propulsion Laboratory, 
California Institute of Technology under a contract with NASA.
This research has made use of the GOLDMine database \citep{goldmine} and the NASA/IPAC Extragalactic Database (NED) 
which is operated by the Jet Propulsion Laboratory, California Institute of Technology, 
under contract with the National Aeronautics and Space Administration. 
We acknowledge the usage of the HyperLeda database (\url{http://leda.univ-lyon1.fr}).
The BCES routine \citep{akritasbershady1996} was run via the python module 
written by Rodrigo Nemmen \citep{nemmen2012}, which is available at \url{https://github.com/rsnemmen/BCES}.
The modified FITEXY linear regressions were performed using the IDL routine MPFITEXY \citep{williams2010}, 
which is available at \url{http://purl.org/mike/mpfitexy}. 
The MPFITEXY routine depends on the MPFIT package \citep{markwardt2009}.
